### 2023-03-09 paper.tex
Write some examples about problems

@@

TODO: maybe an example here about asking chat gpt about a recent event leading to hallucination
and/or asking about a simple mathematical calculation leading to the wrong result

>>>>

\subsection{Vocabulary}
Different model architectures use different vocabularies. These are chosen based
on the differing requirements of the models. The vocabulary needs to accommodate 
multiple languages and proper nouns while using as few tokens as possible per word.
Memory usage also has to be balanced and the number of tokens cannot grow infinitely
large.

@@

For example, when asking ChatGPT, which uses a slightly modified version of GPT-3 called 
GPT-3.5 [citation needed], to do a simple calculation, it answers confidently. 
With a prompt of "\texttt{what is 491*397}" we receive a response of 
"\texttt{The product of 491 and 397 is 195127.}". Unfortunately, using a calculator
leads to a different answer: 194927. Dangerously close, but not quite there.

Another example is asking the model about something they have not been trained on, for
example about future events. Prompting the model with 
"\texttt{What did Sauli Niinistö accomplish during his third term in office?}" returns
a logically perplexing response "\texttt{Sauli Niinistö is the current President of Finland, 
and he is currently serving his second consecutive term in office. 
His third term began on March 1, 2018, and it will end on February 28, 2024. ...}".
The response claims that Sauli Niinistö is currently serving his second term in office
which is correct as of 2023 and also in 2021 where the training data of GPT-3.5 ends 
[citation needed]. However, after this, the response claims that his third term began
in 2018, directly contradicting the previous statement. It is also important to mention
that there has been a two term limit since (insert year here) written into law 
[citation needed, finlex?]. Rest of the response after the first paragraph is removed.

While these limitations can be quite clear to professionals, many people without relevant
experience have no way of discerning factually correct answers from wrong ones. The confidence
by which the models answer can also mislead people into trusting the answers too much.

\section{Problems}
TODO: write about hallucination, overconfidence, radicalization etc.
